DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-12 ase2017/paper.tex
Added implementation section
Added implementation section with reference to CBMC module, description of
instrumentation and CBMC's role as oracle, and all URLs to CBMC 5.7, OVA
and GitHub.

\textcolor{red}{Pascal, can you please review this paragraph?}

\textcolor{blue}{The main development challenge related to \tool is the representation of the
closed-loop control system models, considering FWL effects, time discretization 
and quantization noise.  In particular, our implementation consists of $400$
lines of code related to MATLAB scripts, $585$ and $800$ lines of C code related to the
naive and abstract accelerator backends. In addition, there are $4000$ lines of C code
related to utility functions (e.g., interval and fixed-point arithmetic), $50$ lines
of code to parse MATLAB functions and there are approximately $20$
control system benchmarks to ensure the \tool's regression.  All those artifacts together
with documentation and videos are available in a public github repository,
which is located at \url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.

>>>>

Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system models into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and quantization noise explicitly using CBMC's
nondeterminism API.  Our module was included in CBMC~5.7 and is available for
download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
of our tool is available in a public GitHub
repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
